\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-03 paper/main.tex
.

\subsubsection{Siamese neural networks and modular learnable feature transformation}
As we want to learn from the similarity of drug side effects and
protein phenotypes we opted for a deep siamese network approach, hence
learning a high-dimensional embedding emphasizing this identity by
forcing a similarity between these embeddings. On the other hand we built a deep neural network for the molecular structure based features, also benefiting from the siamese network
architecture. Computing the similarity between two representations, allows for a variety of different methods.
However, we decided for the cosine similarity measure being invariant to scaling.

>>>>

\subsubsection{Siamese neural networks and modular learnable feature transformation}
As we want to learn from the similarity of drug side effects and
protein phenotypes, we use a deep Siamese neural network.
A Siamese neural network aims to learn a similarity between two
embeddings.

learning a high-dimensional embedding emphasizing this identity by
forcing a similarity between these embeddings. On the other hand we
built a deep neural network for the molecular structure based
features, also benefiting from the siamese network
architecture. Computing the similarity between two representations,
allows for a variety of different methods.  However, we decided for
the cosine similarity measure being invariant to scaling.
